Monitoring Time Series With Missing Values:\\a Deep Probabilistic Approach

### 2022-02-17 paper.tex
discussion and future

>>>>

We presented a deep probabilistic architecture for uncertainty
propagation in multivariate time series. This architecture
organically handles two important problems in deep time series
modelling: missing data and multi-step forecasting. Empirical
evaluation demonstrated that our approach outperforms
conventional baselines in terms of forecasting accuracy, while
still being easy to implement. Since, unlike some other
approaches to uncertainty propagation, our architecture
avoids sampling, uncertainty can be propagated efficiently and
represented in closed parametric form, rather than approximated
by samples and posterior intervals.

We confined most of the discussion to the normal uncertainty shape.
Other distributions can be used instead of the normal
distributions where appropriate, provided their parameterization
allows to express a certain observation as well as an uncertain
belief. Analysis of distributions for representing uncertainty
and their feasible parameterization is a subject of ongoing
research. Another research direction worth exploring is
extension of the presented architecture to bidirectional
recurrent neural networks~\cite{BRH15}. Bidirectional RNNs allow
to account for both past and future observations where
appropriate, but make apparently make uncertainty propagation
more complicated. Still, preliminary results suggest that
uncertainty in bidirectional RNNs can be handled in a similar
manner, further facilitating efficient probabilistic uncertainty
propagation in a broader class of deep learning models for time
series.
